Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

\medskip
Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where fluid $1$ Darcy velocity vectors overlapped with fluid saturation are shown. Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.

\medskip
In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, a $2$D domain was used to describe one or more finger formations. These flow instabilities were triggerded from the permeability differences in the domain. Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations. Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more distinct. Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.

>>>>

\medskip
Flow pathways are clearly indicated in Fig.~\ref{fig:3DChannel_planes}, where Darcy velocity vectors overlapped with wetting phase fluid saturation are shown. Fluid displacement occurs mainly in regions of relatively larger permeability, leaving other parts of the domain (\ie regions with low permeability distribution) with little or no momentum, indicating that at these regions the non-wetting fluid (\ie fluid 2) are not effectively displaced.

\medskip
In Sections \ref{section:results:setup}-\ref{section:results_hete_fix_adapt}, finger's formation, growth and branching were triggered by domain heterogeneity represented by permeability differences. Figure~\ref{fig:3DChannel_sat} shows preferential flow pathways at various instances of time.

Using a $3D$ domain, the difference between a flow instability and the preferential flow path that may include smaller fingers is more obvious as the latter may include finger formations. Figure \ref{fig:3DChannel_sat} describes the flow path in various instances of time showing the progression of the saturation front that now becomes more distinct. Heterogeneity is determine by the spatial distribution of porosity ($\phi =0.20$ in the current case) and permeability.
